Vertical shear instability in astrophysical disks: vertically global linear calculations with thermal relaxation and applications to the Solar Nebula

### 2015-03-05 appendix.tex
revised

\section{Linear problem in isothermal limit}\label{iso_discuss}  
Here we examine in more detail the special case of isothermal
perturbations ($\beta\equiv 0$) in the VGSB framework.   
%Isothermal perturbations correspond to $\beta\equiv0$ ($\chi=1$) and 
In this case Eq. \ref{ode_Q} becomes   
\begin{align} 
  Q = W 
\end{align}
(i.e. $\delta P = c_s^2\delta \rho$), and so $  \ii\hat{\sigma}c_s\delta v_z = W^\prime $
from Eq. \ref{lin_vz}. For isothermal perturbations it is in fact
simpler to work with an equation for $W$ by substituting $Q=W$ into
Eq. \ref{ode_w}. We obtain 
\begin{align}
  0 = W^{\prime\prime} + \left[\ln\rho^\prime - \ii \epsilon q \hat{k}
    f(\zhat)\right]W^\prime + \hat{\sigma}^2\left(1+\hat{k}^2\right)W,\label{iso_ode1}
\end{align}
where for discussion purposes we have defined $f(\zhat)$ such that
\begin{align}\label{fz_shear}
  \frac{d\Omega^2}{d\hat{z}} = \epsilon^2q f(\hat{z})\Omega_k^2.
\end{align}
By comparing Eq. \ref{fz_shear} with Eq. \ref{vertical_shear_ex}, we
see that $f(\zhat)= 
\zhat\left(1+\epsilon^2\zhat^2\right)^{-3/2}$. More generally, though,
$f$ may be considered as a representation of the vertical
shear profile. Physically, we expect there is a maximum value of 
$|d\Omega/dz|$. The existence of a maximum, as remarked in
\S\ref{vshear_def}, limits the growth rate of the VSI. We explicitly
demonstrate this below.

>>>>

\section{Linear problem in the isothermal limit}\label{iso_discuss}  
Here we examine in more detail the special case of isothermal
perturbations ($\beta\equiv 0$) in the VGSB framework.   
%Isothermal perturbations correspond to $\beta\equiv0$ ($\chi=1$) and 
In this case Eq. \ref{ode_Q} becomes   
\begin{align} 
  Q = W 
\end{align}
(i.e. $\delta P = c_s^2\delta \rho$), and so $  \ii\hat{\sigma}c_s\delta v_z = W^\prime $
from Eq. \ref{lin_vz}. For isothermal perturbations it is in fact
simpler to work with an equation for $W$ by substituting $Q=W$ into
Eq. \ref{ode_w}. We obtain 
\begin{align}
  0 = W^{\prime\prime} + \left[\ln\rho^\prime - \ii \epsilon q \hat{k}
    f(\zhat)\right]W^\prime + \hat{\sigma}^2\left(1+\hat{k}^2\right)W,\label{iso_ode1}
\end{align}
where for discussion purposes we have defined $f(\zhat)$ such that
\begin{align}\label{fz_shear}
  \frac{d\Omega^2}{d\hat{z}} = \epsilon^2q f(\hat{z})\Omega_k^2.
\end{align}
By comparing Eq. \ref{fz_shear} with Eq. \ref{vertical_shear_ex}, we
see that $f(\zhat)= 
\zhat\left(1+\epsilon^2\zhat^2\right)^{-3/2}$. More generally, though,
$f$ may be considered as a representation of the vertical
shear profile. Physically, we expect there is a maximum value of 
$|d\Omega/dz|$. The existence of a maximum, as remarked in
\S\ref{vshear_def}, limits the growth rate of the VSI. We explicitly
demonstrate this below.
